Fault Classification of Rotating Machinery using Limited Set of Features and k-Nearest Neighbors

### 2024-04-09 iit-src/paper.tex
EDA of stnding fan to calibrate

Our accelerometer ST IIS3DWB mounted to the machine using thin double-sided tape has a wideband 5 kHz linear response sampled at 26.87~kHz. Microcontroller ESP32-POE-ISO stored triaxial 60-second long recordings onto an SD card. In total 48 time series were gathered, 6 in each place. These are split into 5-second intervals for 576 data points overall. Fault labels are missing, therefore we analyze rotational speeds and defective bearing frequencies in the frequency spectrum. The observations form machines are labeled based on source machinery to 4 classes: M1, M2, P1, P2; based on sensor position to 8 classes: M1-1, M1-2, P1-3, P1-4, etc.

@@

Tables~\ref{tab:fsel-methods-td} and \ref{tab:fsel-methods-fd} compare the average 5-fold test accuracy of different feature selection methods for the k-NN model with k = 5. Three-axis features have better accuracy for original classes but perform worse than single axes after relabeling for high-severity faults.

>>>>

Our accelerometer ST IIS3DWB mounted to the machine using thin double-sided tape has a wideband 5 kHz linear response sampled at 26.87~kHz. Microcontroller ESP32-POE-ISO stored triaxial 60-second long recordings onto an SD card. In total 48 time series were gathered, 6 in each place. These are split into 5-second intervals for 576 data points overall. Fault labels are missing, therefore we analyze rotational speeds and defective bearing frequencies in the frequency spectrum. The observations from machines are labeled based on source machinery to 4 classes: M1, M2, P1, P2; based on sensor position to 8 classes: M1-1, M1-2, P1-3, P1-4, etc.

@@

Tables~\ref{tab:fsel-methods-td} and \ref{tab:fsel-methods-fd} compare the average 5-fold test accuracy of different feature selection methods for the k-NN model with k = 5. Three-axis features reach better accuracy the one-axis ones.
